### 2009-10-19 doc/tech_doc/client/job_description_mapping.tex
Updating job description mapping document.

\documentclass{article}
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{multirow}

@@

\section{XRSL mapping}
\begin{table}
\begin{center}
\begin{tabular}{l|c|c}
XRSL input  & Internal representaion & XRSL output\\\hline
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles & DataStaging.File.Name DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & TODO & TODO\\
outputFiles & DataStaging.File.Name DataStaging.File.Target & outputFiles\\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Not mapped & Not mapped\\
benchmarks & Not mapped & Not mapped\\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout outputFiles\\
stderr & Application.Error & stderr outputFiles\\
join & Application.Join & Not mapped\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads DataStaging.File.Target.Threads & Not mapped\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & Not mapped\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & Not mapped\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & DataStaging.File.DataIndexingService & Not mapped\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & Not mapped\\
dryRun & Not mapped & Not mapped\\
rsl\_substitution & Processed internally by the parser & Not mapped\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabular}
\end{center}
\end{table}

\section{JDL mapping}
\begin{table}
\begin{center}
\begin{tabular}{l|c|c}
JDL input  & Internal representaion & JDL output\\\hline
JobType & Not mapped & Not mapped\\
Executable & Application.Executable.Name & Executable InputSandbox\\
Arguments & Application.Executable.Arguments & Arguments\\
StdInput & Application.Input & StdInput InputSandbox\\
StdOutput & Application.Output & StdOutput OutputSandbox OutputSandboxDestURI\\
StdError & Application.Error & StdError OutputSandbox OutputSandboxDestURI\\
InputSandbox & DataStaging.File.Name DataStaging.File.Source & InputSandbox\\
InputSandboxBaseURI & DataStaging.File.Source.URI & InputSandbox\\
OutputSandbox & DataStaging.File.Name DataStaging.File.Target.URI & OutputSandbox OutputSandboxDestURI\\
OutputSandboxDestURI & DataStaging.File.Target DataStaging.File.KeepData & OutputSandbox OutputSandboxDestURI\\
OutputSandboxBaseDestURI & DataStaging.File.Target.URI & OutputSandbox OutputSandboxDestURI\\
Prologue & Application.Prologue.Name & Prologue\\
PrologueArguments & Application.Prologue.Arguments & PrologueArguments\\
Epilogue & Application.Epilogue.Name & Epilogue\\
EpilogueArguments & Application.Epilogue.Arguments & EpilogueArguments\\
AllowZippedISB & Stored internally, not processed & AllowZippedISB\\
ZippedISB & Stored internally, not processed & ZippedISB\\
ExpiryTime & Application.ExpiryTime & ExpiryTime\\
Environment & Application.Environment & Environment\\
PerusalFileEnable & Stored internally, not processed & PerusalFileEnable\\
PerusalTimeInterval & Stored internally, not processed & PerusalTimeInterval\\
PerusalFilesDestURI & Stored internally, not processed & PerusalFilesDestURI\\
InputData (Deprecated) & Not mapped & Not mapped\\
OutputData (Deprecated) & Not mapped & Not mapped\\
StorageIndex (Deprecated) & Not mapped & Not mapped\\
DataCatalog (Deprecated) & Not mapped & Not mapped\\
DataRequirements & Stored internally, not processed & DataRequirements\\
DataAccessProtocol & Stored internally, not processed & DataAccessProtocol\\
OutputSE & Stored internally, not processed & OutputSE\\
VirtualOrganisation & Identification.JobVOName & VirtualOrganisation\\
RetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
ShallowRetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
LBAddress & Stored internally, not processed & LBAddress\\
MyProxyServer & Application.CredentialService & MyProxyServer\\
HLRLocation & Stored internally, not processed & HLRLocation\\
JobProvenance & Stored internally, not processed & JobProvenance\\
NodeNumber & Stored internally, not processed & NodeNumber\\
JobSteps (Deprecated) & Not mapped & Not mapped\\
CurrentStep (Deprecated) & Not mapped & Not mapped\\
JobState (Deprecated) & Not mapped & Not mapped\\
ListenerPort & Stored internally, not processed & ListenerPort\\
ListenerHost & Stored internally, not processed & ListenerHost\\
ListenerPipeName & Stored internally, not processed & ListenerPipeName\\
Requirements & Stored internally, not processed & Requirements\\
Rank & JobMeta.Rank & Rank\\
FuzzyRank & JobMeta.FuzzyRank & FuzzyRank\\
UserTags & Identification.UserTag & UserTags\\
BatchSystem & Stored internally, not processed & BatchSystem\\
QueueName & Resources.CandidateTarget.QueueName & QueueName\\
\end{tabular}
\end{center}
\end{table}

\section{JSDL mapping}
\begin{table}
\begin{center}
\begin{tabular}{l|c|c}
JSDL input  & Internal representaion & JSDL output\\\hline
\bfseries JobIdentification & &\\
JobName & &\\
JobAnnotation & &\\
JobProject & &\\
\bfseries Application & &\\
ApplicationName & &\\
ApplicationVersion & &\\
\bfseries Resources & &\\
CandidateHosts/HostName & &\\
FileSystem/FileSystemType & &\\
FileSystem/Description & &\\
FileSystem/MountPoint & &\\
FileSystem/DiskSpace & &\\
ExclusiveExecution & &\\
OperatingSystem/OperatingSystemType/OperatingSystemName & &\\
OperatingSystem/OperatingSystemVersion & &\\
CPUArchitecture/CPUArchitectureName & &\\
IndividualCPUSpeed & &\\
IndividualCPUTime & &\\
IndividualCPUCount & &\\
IndividualNetworkBandwidth & &\\
IndividualPhysicalMemory & &\\
IndividualVirtualMemory & &\\
IndividualDiskSpace & &\\
TotalCPUTime & &\\
TotalCPUCount & &\\
TotalPhysicalMemory & &\\
TotalVirtualMemory & &\\
TotalDiskSpace & &\\
TotalResourceCount & &\\
\bfseries DataStaging & {}-{}- & {}-{}-\\
FileName & &\\
FileSystemName & &\\
CreationFlag & &\\
DeleteOnTermination & &\\
Source/URI & &\\
Target/URI & &\\
\end{tabular}
\end{center}
\end{table}

\section{POSIX-JSDL mapping}
\begin{table}
\begin{center}
\begin{tabular}{l|c|c}
POSIX-JSDL input  & Internal representation & POSIX-JSDL output\\\hline
Executable & &\\
Argument & &\\
Input & &\\
Output & &\\
Error & &\\
WorkingDirectory & &\\
Environment & &\\
WallTimeLimit & &\\
FileSizeLimit & &\\
CoreDumpLimit & &\\
DataSegmentLimit & &\\
LockedMemoryLimit & &\\
OpenDescriptorsLimit & &\\
PipeSizeLimit & &\\
StackSizeLimit & &\\
CPUTimeLimit & &\\
ProcessCountLimit & &\\
VirtualMemoryLimit & &\\
ThreadCountLimit & &\\
UserName & &\\
GroupName & &\\
\end{tabular}
\end{center}
\end{table}

\section{HPCProfile-JSDL mapping}
\begin{table}
\begin{center}
\begin{tabular}{l|c|c}
HPCProfile-JSDL input  & Internal representaion & HPCProfile-JSDL output\\\hline
Executable & & \\
Argument & & \\
Input & & \\
Output & & \\
Error & & \\
WorkingDirectory & &\\
Environment & &\\
UserName & &\\
\end{tabular}
\end{center}
\end{table}
\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
%~ \usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{array}
\usepackage{booktabs}
\usepackage{ltablex}
\usepackage[english]{babel}
\usepackage{multirow}
\usepackage[table]{xcolor} % Note: The rowcolors command does not work properly with the tabularx environment.

\colorlet{tableheadcolor}{gray!25}
\colorlet{tablerowcolor}{gray!12.5}

\newcolumntype{C}{>{\ttfamily\footnotesize}c}
\newcolumntype{T}{>{\ttfamily\footnotesize\centering\arraybackslash}X}

\newcommand{\TODO}{\normalsize{\textnormal{TODO}}}
\newcommand{\NM}{\normalsize{\textnormal{Not mapped}}}
\newcommand{\NST}[1]{\normalsize{\textnormal{#1}}}
\newcommand{\defineheadfoot}{\endfirsthead %
\midrule %
\multicolumn{3}{c}{Continued from previous page}\\%
\midrule %
\endhead %
\midrule %
\multicolumn{3}{c}{Continues at next page}\\%
\midrule %
\endfoot %
\bottomrule %
\endlastfoot}

\renewcommand{\tabularxcolumn}[1]{m{#1}}

@@

\section{XRSL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CTC}
\toprule
\NST{XRSL input} & \NST{Internal representaion} & \NST{XRSL output}\\
\midrule
\defineheadfoot
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles& DataStaging.File.Name,\linebreak DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & \TODO & \TODO \\
outputFiles & DataStaging.File.Name,\linebreak DataStaging.File.Target & outputFiles \\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Resources.TotalCPUTime & \NM \\
benchmarks & Resources.TotalCPUTime & \NM \\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout, outputFiles\\
stderr & Application.Error & stderr, outputFiles\\
join & Application.Join & \NM\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads,\linebreak DataStaging.File.Target.Threads & \NM\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & \NM\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & \NM\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & DataStaging.File.DataIndexingService & \NM\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & \NM\\
dryRun & \NM & \NM\\
rsl\_substitution & \NST{Processed internally by the parser} & \NM\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabularx}
\end{center}

\section{JDL mapping}
\begin{center}
\rowcolors{3}{}{tablerowcolor}
\begin{tabularx}{\textwidth}{CTT}
\toprule
\rowcolor{white}
\NST{JDL input} & \NST{Internal representaion} & \NST{JDL output}\\
\midrule
\defineheadfoot
JobType & \NM & \NM\\
Executable & Application.Executable.Name & Executable, InputSandbox\\
Arguments & Application.Executable.Arguments & Arguments\\
StdInput & Application.Input & StdInput,\linebreak InputSandbox\\
StdOutput & Application.Output & StdOutput,\linebreak OutputSandbox,\linebreak OutputSandboxDestURI\\
StdError & Application.Error & StdError,\linebreak OutputSandbox,\linebreak OutputSandboxDestURI\\
InputSandbox & DataStaging.File.Name,\linebreak DataStaging.File.Source & InputSandbox\\
InputSandboxBaseURI & DataStaging.File.Source.URI & InputSandbox\\
OutputSandbox & DataStaging.File.Name,\linebreak DataStaging.File.Target.URI & OutputSandbox,\linebreak OutputSandboxDestURI\\
OutputSandboxDestURI & DataStaging.File.Target,\linebreak DataStaging.File.KeepData & OutputSandbox,\linebreak OutputSandboxDestURI\\
OutputSandboxBaseDestURI & DataStaging.File.Target.URI & OutputSandbox,\linebreak OutputSandboxDestURI\\
Prologue & Application.Prologue.Name & Prologue\\
PrologueArguments & Application.Prologue.Arguments & PrologueArguments\\
Epilogue & Application.Epilogue.Name & Epilogue\\
EpilogueArguments & Application.Epilogue.Arguments & EpilogueArguments\\
AllowZippedISB & Stored internally, not processed & AllowZippedISB\\
ZippedISB & Stored internally, not processed & ZippedISB\\
ExpiryTime & Application.ExpiryTime & ExpiryTime\\
Environment & Application.Environment & Environment\\
PerusalFileEnable & \NST{Stored internally, not processed} & PerusalFileEnable\\
PerusalTimeInterval & \NST{Stored internally, not processed} & PerusalTimeInterval\\
PerusalFilesDestURI & \NST{Stored internally, not processed} & PerusalFilesDestURI\\
InputData \NST{(Deprecated)} & \NM & \NM\\
OutputData \NST{(Deprecated)} & \NM & \NM\\
StorageIndex \NST{(Deprecated)} & \NM & \NM\\
DataCatalog \NST{(Deprecated)} & \NM & \NM\\
DataRequirements & \NST{Stored internally, not processed} & DataRequirements\\
DataAccessProtocol & \NST{Stored internally, not processed} & DataAccessProtocol\\
OutputSE & \NST{Stored internally, not processed} & OutputSE\\
VirtualOrganisation & Identification.JobVOName & VirtualOrganisation\\
RetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
ShallowRetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
LBAddress & \NST{Stored internally, not processed} & LBAddress\\
MyProxyServer & Application.CredentialService & MyProxyServer\\
HLRLocation & \NST{Stored internally, not processed} & HLRLocation\\
JobProvenance & \NST{Stored internally, not processed} & JobProvenance\\
NodeNumber & \NST{Stored internally, not processed} & NodeNumber\\
JobSteps \NST{(Deprecated)} & \NM & \NM\\
CurrentStep \NST{(Deprecated)} & \NM & \NM\\
JobState \NST{(Deprecated)} & \NM & \NM\\
ListenerPort & \NST{Stored internally, not processed} & ListenerPort\\
ListenerHost & \NST{Stored internally, not processed} & ListenerHost\\
ListenerPipeName & \NST{Stored internally, not processed} & ListenerPipeName\\
Requirements & \NST{Stored internally, not processed} & Requirements\\
Rank & JobMeta.Rank & Rank\\
FuzzyRank & JobMeta.FuzzyRank & FuzzyRank\\
UserTags & Identification.UserTag & UserTags\\
BatchSystem & \NST{Stored internally, not processed} & BatchSystem\\
QueueName & Resources.CandidateTarget.QueueName & QueueName
\end{tabularx}
\end{center}

\section{JSDL mapping}
\begin{center}
\rowcolors{3}{}{tablerowcolor}
\begin{tabularx}{400pt}{TCC}
\toprule
\NST{JSDL input} & \NST{Internal representaion} & \NST{JSDL output}\\
\midrule
\defineheadfoot
\multicolumn{3}{c}{\bfseries JobIdentification}\\
\midrule
JobName & &\\
JobAnnotation & &\\
JobProject & &\\
\midrule
\multicolumn{3}{c}{\bfseries Application}\\
\midrule
ApplicationName & &\\
ApplicationVersion & &\\
\midrule
\multicolumn{3}{c}{\bfseries Resources}\\
\midrule
CandidateHosts/HostName & &\\
FileSystem/FileSystemType & &\\
FileSystem/Description & &\\
FileSystem/MountPoint & &\\
FileSystem/DiskSpace & &\\
ExclusiveExecution & &\\
OperatingSystem/\linebreak OperatingSystemType/\linebreak OperatingSystemName & &\\
OperatingSystem/\linebreak OperatingSystemVersion & &\\
CPUArchitecture/\linebreak CPUArchitectureName & &\\
IndividualCPUSpeed & &\\
IndividualCPUTime & &\\
IndividualCPUCount & &\\
IndividualNetworkBandwidth & &\\
IndividualPhysicalMemory & &\\
IndividualVirtualMemory & &\\
IndividualDiskSpace & &\\
TotalCPUTime & &\\
TotalCPUCount & &\\
TotalPhysicalMemory & &\\
TotalVirtualMemory & &\\
TotalDiskSpace & &\\
TotalResourceCount & &\\
\midrule
\multicolumn{3}{c}{\bfseries DataStaging}\\
\midrule
FileName & &\\
FileSystemName & &\\
CreationFlag & &\\
DeleteOnTermination & &\\
Source/URI & &\\
Target/URI & &\\
\end{tabularx}
\end{center}

\section{POSIX-JSDL mapping}
\begin{center}
\rowcolors{3}{}{tablerowcolor}
\begin{tabularx}{400pt}{CCC}
\toprule
\NST{POSIX-JSDL input} & \NST{Internal representation} & \NST{POSIX-JSDL output}\\
\midrule
\defineheadfoot
Executable & &\\
Argument & &\\
Input & &\\
Output & &\\
Error & &\\
WorkingDirectory & &\\
Environment & &\\
WallTimeLimit & &\\
FileSizeLimit & &\\
CoreDumpLimit & &\\
DataSegmentLimit & &\\
LockedMemoryLimit & &\\
OpenDescriptorsLimit & &\\
PipeSizeLimit & &\\
StackSizeLimit & &\\
CPUTimeLimit & &\\
ProcessCountLimit & &\\
VirtualMemoryLimit & &\\
ThreadCountLimit & &\\
UserName & &\\
GroupName & &\\
\end{tabularx}
\end{center}

\section{HPCProfile-JSDL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CCC}
\toprule
\NST{HPCProfile-JSDL input}  & \NST{Internal representaion} & \NST{HPCProfile-JSDL output}\\
\midrule
\defineheadfoot
Executable & & \\
Argument & & \\
Input & & \\
Output & & \\
Error & & \\
WorkingDirectory & &\\
Environment & &\\
UserName & &\\
\end{tabularx}
\end{center}
\end{document}
